Stats

### 2022-03-23 stats/analysis.Rmd
add proper splithalf section, change order in variation section

```{r splithalfr_hedge_kids}
fn_score_hedge <- function(ds) {
  return(mean(clickDistInBalloons, na.rm = TRUE))
}

@@

# random split
splitscores_hedge_random_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

hedge_random_kids <- split_coefs(splitscores_hedge_random_kids, cor)
hedge_random_kids_ci  <- split_ci(splitscores_hedge_random_kids, cor)

# create dataframe to save data
splithalf_data <- tibble(
                    studyversion = "hedge", 
                    sample = "kids", 
                    split = "random", 
                    stratification = "none", 
                    mean = hedge_random_kids, 
                    CI_lower = hedge_random_kids_ci$lims["0.025","bca"], 
                    CI_upper = hedge_random_kids_ci$lims["0.975","bca"])

# random split with stratification by target position
splitscores_hedge_randomStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

hedge_randomStrat_kids <- split_coefs(splitscores_hedge_randomStrat_kids, cor)
hedge_randomStrat_kids_ci <- split_ci(splitscores_hedge_randomStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "kids", 
                                        split = "random",
                                        stratification = "target position",
                                        mean = hedge_randomStrat_kids, 
                                        CI_lower = hedge_randomStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_randomStrat_kids_ci$lims["0.975","bca"]
                                      )

# odd even split
splitscores_hedge_oddeven_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("odd_even"),
)

@@

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "kids", 
                                        split = "odd even", 
                                        stratification = "none", 
                                        mean = hedge_oddeven_kids, 
                                        CI_lower = hedge_oddeven_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddeven_kids_ci$lims["0.975","bca"]
                                      )

# odd even split with stratification by target position
splitscores_hedge_oddevenStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
  replications = 1,
  method = c("odd_even"),
)

@@

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "kids", 
                                        split = "odd even",
                                        stratification = "target position",
                                        mean = hedge_oddevenStrat_kids, 
                                        CI_lower = hedge_oddevenStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddevenStrat_kids_ci$lims["0.975","bca"]
                                      )

# first second testhalves split
splitscores_hedge_firstsecond_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("first_second"),
)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "kids", 
                                        split = "first second", 
                                        stratification = "none",                                        
                                        mean = hedge_firstsecond_kids, 
                                        CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
                                      )

# first second testhalves split with stratification by target position
splitscores_hedge_firstsecondStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
  replications = 1,
  method = c("odd_even"),
)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "kids", 
                                        split = "first second",
                                        stratification = "target position",
                                        mean = hedge_firstsecondStrat_kids, 
                                        CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
                                      )
```

```{r splithalfr_hedge_adults}
# random split
splitscores_hedge_random_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

hedge_random_adults <- split_coefs(splitscores_hedge_random_adults, cor)
hedge_random_adults_ci  <- split_ci(splitscores_hedge_random_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "adults", 
                                        split = "random", 
                                        stratification = "none", 
                                        mean = hedge_random_adults, 
                                        CI_lower = hedge_random_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_random_adults_ci$lims["0.975","bca"]
                                      )

# random split with stratification by target position
splitscores_hedge_randomStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

hedge_randomStrat_adults <- split_coefs(splitscores_hedge_randomStrat_adults, cor)
hedge_randomStrat_adults_ci <- split_ci(splitscores_hedge_randomStrat_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "adults", 
                                        split = "random",
                                        stratification = "target position",
                                        mean = hedge_randomStrat_adults, 
                                        CI_lower = hedge_randomStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_randomStrat_adults_ci$lims["0.975","bca"]
                                      )

# odd even split
splitscores_hedge_oddeven_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("odd_even"),
)

@@

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "adults", 
                                        split = "odd even", 
                                        stratification = "none", 
                                        mean = hedge_oddeven_adults, 
                                        CI_lower = hedge_oddeven_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddeven_adults_ci$lims["0.975","bca"]
                                      )

# odd even split with stratification by target position
splitscores_hedge_oddevenStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
  replications = 1,
  method = c("odd_even"),
)

@@

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "adults", 
                                        split = "odd even",
                                        stratification = "target position",
                                        mean = hedge_oddevenStrat_adults, 
                                        CI_lower = hedge_oddevenStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddevenStrat_adults_ci$lims["0.975","bca"]
                                      )

# first second testhalves split
splitscores_hedge_firstsecond_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("first_second"),
)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "adults", 
                                        split = "first second", 
                                        stratification = "none",                                        
                                        mean = hedge_firstsecond_adults, 
                                        CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
                                      )

# first second testhalves split with stratification by target position
splitscores_hedge_firstsecondStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
  replications = 1,
  method = c("odd_even"),
)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "adults", 
                                        split = "first second",
                                        stratification = "target position",
                                        mean = hedge_firstsecondStrat_adults, 
                                        CI_lower = hedge_firstsecondStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_firstsecondStrat_adults_ci$lims["0.975","bca"]
                                      )
```

@@

box_intCon_data %>% 
  group_by(subjID, targetPosition) %>% 
  summarise(n = n()) %>% 
  filter(n < 2)

# random split
splitscores_box_random_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

box_random_kids <- split_coefs(splitscores_box_random_kids, cor)
box_random_kids_ci  <- split_ci(splitscores_box_random_kids, cor)

# create dataframe to save data
splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "kids", 
                                        split = "random", 
                                        stratification = "none", 
                                        mean = box_random_kids, 
                                        CI_lower = box_random_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_random_kids_ci$lims["0.975","bca"])

# random split with stratification by target position
splitscores_box_randomStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  careful = FALSE, 
)

box_randomStrat_kids <- split_coefs(splitscores_box_randomStrat_kids, cor)
box_randomStrat_kids_ci <- split_ci(splitscores_box_randomStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "kids", 
                                        split = "random",
                                        stratification = "target position",
                                        mean = box_randomStrat_kids, 
                                        CI_lower = box_randomStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_randomStrat_kids_ci$lims["0.975","bca"]
                                      )

# odd even split
splitscores_box_oddeven_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("odd_even"),
)

@@

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "kids", 
                                        split = "odd even", 
                                        stratification = "none", 
                                        mean = box_oddeven_kids, 
                                        CI_lower = box_oddeven_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_oddeven_kids_ci$lims["0.975","bca"]
                                      )

# odd even split with stratification by target position
splitscores_box_oddevenStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  # careful = FALSE
)

@@

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "kids", 
                                        split = "odd even",
                                        stratification = "target position",
                                        mean = box_oddevenStrat_kids, 
                                        CI_lower = box_oddevenStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_oddevenStrat_kids_ci$lims["0.975","bca"]
                                      )

# first second testhalves split
splitscores_box_firstsecond_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("first_second"),
)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "kids", 
                                        split = "first second", 
                                        stratification = "none",                                        
                                        mean = box_firstsecond_kids, 
                                        CI_lower = box_firstsecond_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_firstsecond_kids_ci$lims["0.975","bca"]
                                      )

# first second testhalves split with stratification by target position
splitscores_box_firstsecondStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  # careful = FALSE,
)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "kids", 
                                        split = "first second",
                                        stratification = "target position",
                                        mean = box_firstsecondStrat_kids, 
                                        CI_lower = box_firstsecondStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_firstsecondStrat_kids_ci$lims["0.975","bca"]
                                      )
```

```{r splithalfr_box_adults}
# random split
splitscores_box_random_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

box_random_adults <- split_coefs(splitscores_box_random_adults, cor)
box_random_adults_ci  <- split_ci(splitscores_box_random_adults, cor)

>>>>

```{r splithalfr_hedge_kids}
fn_score_hedge <- function(ds) {
  return(mean(ds$clickDistInBalloons, na.rm = TRUE))
}

@@

# first-second half split
splitscores_hedge_firstsecond_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("first_second"),
  ncores = 1,
  verbose = F
)

splithalf_data <- tibble(
                          sample = "kids", 
                          studyversion = "hedge", 
                          method = "first-second", 
                          stratification = "none",                                        
                          coefficient = hedge_firstsecond_kids, 
                          CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"], 
                          CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
                        )

# first-second half stratified by target position
splitscores_hedge_firstsecondStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("first_second"),
  ncores = 1,
  verbose = F, 
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "first-second",
                                        stratification = "target position",
                                        coefficient = hedge_firstsecondStrat_kids,
                                        CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
                                      )

# odd-even split
splitscores_hedge_oddeven_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("odd_even"),
  ncores = 1,
  verbose = F
)

@@

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "odd-even",
                                        stratification = "none",
                                        coefficient = hedge_oddeven_kids,
                                        CI_lower = hedge_oddeven_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddeven_kids_ci$lims["0.975","bca"]
                                      )

# odd-even split stratified by target position
splitscores_hedge_oddevenStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("odd_even"),
  ncores = 1,
  verbose = F, 
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

@@

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "odd-even",
                                        stratification = "target position",
                                        coefficient = hedge_oddevenStrat_kids,
                                        CI_lower = hedge_oddevenStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddevenStrat_kids_ci$lims["0.975","bca"]
                                      )

# permutated splitting (random sampling without replacement)
splitscores_hedge_permutated_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
)

hedge_permutated_kids <- split_coefs(splitscores_hedge_permutated_kids, cor)
hedge_permutated_kids_ci <- split_ci(splitscores_hedge_permutated_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "permutated",
                                        stratification = "none",
                                        coefficient = hedge_permutated_kids,
                                        CI_lower = hedge_permutated_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_permutated_kids_ci$lims["0.975","bca"]
                                      )

# permutated splitting stratified by target position
splitscores_hedge_permutatedStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

hedge_permutatedStrat_kids <- split_coefs(splitscores_hedge_permutatedStrat_kids, cor)
hedge_permutatedStrat_kids_ci <- split_ci(splitscores_hedge_permutatedStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "permutated",
                                        stratification = "target position",
                                        coefficient = hedge_permutatedStrat_kids,
                                        CI_lower = hedge_permutatedStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_permutatedStrat_kids_ci$lims["0.975","bca"]
                                      )

# monte carlo (sampling with replacement)
splitscores_hedge_montecarlo_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
  replace = TRUE,
)

hedge_montecarlo_kids <- split_coefs(splitscores_hedge_montecarlo_kids, cor)
hedge_montecarlo_kids_ci <- split_ci(splitscores_hedge_montecarlo_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "Monte Carlo",
                                        stratification = "none",
                                        coefficient = hedge_montecarlo_kids,
                                        CI_lower = hedge_montecarlo_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_montecarlo_kids_ci$lims["0.975","bca"]
                                      )

# monte carlo stratified by target position
splitscores_hedge_montecarloStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
  replace = TRUE,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

hedge_montecarloStrat_kids <- split_coefs(splitscores_hedge_montecarloStrat_kids, cor)
hedge_montecarloStrat_kids_ci <- split_ci(splitscores_hedge_montecarloStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "Monte Carlo",
                                        stratification = "target position",
                                        coefficient = hedge_montecarloStrat_kids,
                                        CI_lower = hedge_montecarloStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_montecarloStrat_kids_ci$lims["0.975","bca"]
                                      )
```

```{r splithalfr_hedge_adults}
# first-second half split
splitscores_hedge_firstsecond_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("first_second"),
  ncores = 1,
  verbose = F
)

splithalf_data <- splithalf_data %>% add_row(
                                              sample = "adults", 
                                              studyversion = "hedge", 
                                              method = "first-second", 
                                              stratification = "none",                                        
                                              coefficient = hedge_firstsecond_adults, 
                                              CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"], 
                                              CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
                                            )

# first-second half stratified by target position
splitscores_hedge_firstsecondStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("first_second"),
  ncores = 1,
  verbose = F, 
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "adults", 
                                        studyversion = "hedge", 
                                        method = "first-second",
                                        stratification = "target position",
                                        coefficient = hedge_firstsecondStrat_adults,
                                        CI_lower = hedge_firstsecondStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_firstsecondStrat_adults_ci$lims["0.975","bca"]
                                      )

# odd-even split
splitscores_hedge_oddeven_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("odd_even"),
  ncores = 1,
  verbose = F
)

@@

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "adults", 
                                        studyversion = "hedge", 
                                        method = "odd-even",
                                        stratification = "none",
                                        coefficient = hedge_oddeven_adults,
                                        CI_lower = hedge_oddeven_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddeven_adults_ci$lims["0.975","bca"]
                                      )

# odd-even split stratified by target position
splitscores_hedge_oddevenStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("odd_even"),
  ncores = 1,
  verbose = F, 
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

@@

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "adults", 
                                        studyversion = "hedge", 
                                        method = "odd-even",
                                        stratification = "target position",
                                        coefficient = hedge_oddevenStrat_adults,
                                        CI_lower = hedge_oddevenStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddevenStrat_adults_ci$lims["0.975","bca"]
                                      )

# permutated splitting (random sampling without replacement)
splitscores_hedge_permutated_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
)

hedge_permutated_adults <- split_coefs(splitscores_hedge_permutated_adults, cor)
hedge_permutated_adults_ci <- split_ci(splitscores_hedge_permutated_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "adults", 
                                        studyversion = "hedge", 
                                        method = "permutated",
                                        stratification = "none",
                                        coefficient = hedge_permutated_adults,
                                        CI_lower = hedge_permutated_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_permutated_adults_ci$lims["0.975","bca"]
                                      )

# permutated splitting stratified by target position
splitscores_hedge_permutatedStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

hedge_permutatedStrat_adults <- split_coefs(splitscores_hedge_permutatedStrat_adults, cor)
hedge_permutatedStrat_adults_ci <- split_ci(splitscores_hedge_permutatedStrat_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "adults", 
                                        studyversion = "hedge", 
                                        method = "permutated",
                                        stratification = "target position",
                                        coefficient = hedge_permutatedStrat_adults,
                                        CI_lower = hedge_permutatedStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_permutatedStrat_adults_ci$lims["0.975","bca"]
                                      )

# monte carlo (sampling with replacement)
splitscores_hedge_montecarlo_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
  replace = TRUE,
)

hedge_montecarlo_adults <- split_coefs(splitscores_hedge_montecarlo_adults, cor)
hedge_montecarlo_adults_ci <- split_ci(splitscores_hedge_montecarlo_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "adults", 
                                        studyversion = "hedge", 
                                        method = "Monte Carlo",
                                        stratification = "none",
                                        coefficient = hedge_montecarlo_adults,
                                        CI_lower = hedge_montecarlo_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_montecarlo_adults_ci$lims["0.975","bca"]
                                      )

# monte carlo stratified by target position
splitscores_hedge_montecarloStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
  replace = TRUE,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

hedge_montecarloStrat_adults <- split_coefs(splitscores_hedge_montecarloStrat_adults, cor)
hedge_montecarloStrat_adults_ci <- split_ci(splitscores_hedge_montecarloStrat_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "adults", 
                                        studyversion = "hedge", 
                                        method = "Monte Carlo",
                                        stratification = "target position",
                                        coefficient = hedge_montecarloStrat_adults,
                                        CI_lower = hedge_montecarloStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_montecarloStrat_adults_ci$lims["0.975","bca"]
                                      )
```

@@

# first-second half split
splitscores_box_firstsecond_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  method = c("first_second"),
  ncores = 1,
  verbose = F
)

splithalf_data <- splithalf_data %>% add_row(
                                              sample = "kids", 
                                              studyversion = "box", 
                                              method = "first-second", 
                                              stratification = "none",                                        
                                              coefficient = box_firstsecond_kids, 
                                              CI_lower = box_firstsecond_kids_ci$lims["0.025","bca"], 
                                              CI_upper = box_firstsecond_kids_ci$lims["0.975","bca"]
                                            )

# first-second half stratified by target position
splitscores_box_firstsecondStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  method = c("first_second"),
  ncores = 1,
  verbose = F, 
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "box", 
                                        method = "first-second",
                                        stratification = "target position",
                                        coefficient = box_firstsecondStrat_kids,
                                        CI_lower = box_firstsecondStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_firstsecondStrat_kids_ci$lims["0.975","bca"]
                                      )

# odd-even split
splitscores_box_oddeven_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  method = c("odd_even"),
  ncores = 1,
  verbose = F
)

@@

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "box", 
                                        method = "odd-even",
                                        stratification = "none",
                                        coefficient = box_oddeven_kids,
                                        CI_lower = box_oddeven_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_oddeven_kids_ci$lims["0.975","bca"]
                                      )

# odd-even split stratified by target position
splitscores_box_oddevenStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  method = c("odd_even"),
  ncores = 1,
  verbose = F, 
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

@@

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "box", 
                                        method = "odd-even",
                                        stratification = "target position",
                                        coefficient = box_oddevenStrat_kids,
                                        CI_lower = box_oddevenStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_oddevenStrat_kids_ci$lims["0.975","bca"]
                                      )

# permutated splitting (random sampling without replacement)
splitscores_box_permutated_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
)

box_permutated_kids <- split_coefs(splitscores_box_permutated_kids, cor)
box_permutated_kids_ci <- split_ci(splitscores_box_permutated_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "box", 
                                        method = "permutated",
                                        stratification = "none",
                                        coefficient = box_permutated_kids,
                                        CI_lower = box_permutated_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_permutated_kids_ci$lims["0.975","bca"]
                                      )

# permutated splitting stratified by target position
splitscores_box_permutatedStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

box_permutatedStrat_kids <- split_coefs(splitscores_box_permutatedStrat_kids, cor)
box_permutatedStrat_kids_ci <- split_ci(splitscores_box_permutatedStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "box", 
                                        method = "permutated",
                                        stratification = "target position",
                                        coefficient = box_permutatedStrat_kids,
                                        CI_lower = box_permutatedStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_permutatedStrat_kids_ci$lims["0.975","bca"]
                                      )
